The Evolution of Phenotypically Invariant Genetic Networks

### 2021-05-03 title_page_revision.tex
made title page

{\centering
{\Huge \bf System drift and speciation} \\ \vspace{0.75cm}
Joshua S. Schiffman$^{\dagger}$ \qquad Peter L. Ralph$^{\ddagger}$ \\ \vspace{0.5cm}
$^{\dagger}${\footnotesize {New York Genome Center, New York, New York 10013, U.S.A \& Weill Cornell Medicine, New York, New York 10065, USA  \\
$^{\ddagger}$Departments of Mathematics and Biology \& The Institute for Ecology and Evolution, University of Oregon, Eugene, Oregon 97403, USA}} \\ \vspace{0.5cm}
{\small \texttt{jschiffman@nygenome.org} \qquad 
\texttt{plr@uoregon.edu}} \\ \vspace{0.5cm}
%\small \today \\
\vspace{0.25cm}
}

>>>>

{\centering
{\Huge \bf System drift and speciation} \\ \vspace{0.75cm}
Joshua S. Schiffman$^{\dagger \ast}$ \qquad Peter L. Ralph$^{\ddagger \ast}$ \\ \vspace{0.5cm}
$^{\dagger}${\footnotesize {Current affiliations: New York Genome Center, NY, NY 10013 \& Weill Cornell Medicine, NY, NY 10065  \\
$^{\ddagger}$Departments of Mathematics and Biology \& The Institute for Ecology and Evolution, University of Oregon, Eugene, OR 97403 \\ 
$^{\ast}$Work conducted at: Molecular and Computational Biology, University of Southern California, LA, CA 90089} } \\ \vspace{0.5cm}
{\small \texttt{jschiffman@nygenome.org} \qquad 
\texttt{plr@uoregon.edu}} \\ \vspace{0.5cm}
%\small \today \\
\vspace{0.25cm}
}
